Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms

### 2016-02-10 podc16/paper2.tex
trivial changes

We consider a set of processes $P$ subject to crash-stop faults and communicating by message-passing in an asynchronous network. Processes in $P$ must solve the Generalized Consensus problem~\cite{lamport-generalized}. Each process receives proposals for commands of the form \texttt{Propose}$(c)$, and it produces responses of the form \texttt{Decide}$(\sigma)$, where $\sigma$ is a c-struct. A c-struct set is a set, containing the element $\bot$, with an append operator $\bullet$ such that $\sigma \bullet c$ is a c-struct, for any c-struct $\sigma$ and command $c$. We say that two commands \textit{commute} when $\sigma\bullet c_1\bullet c_2 =  \sigma\bullet c_2\bullet c_1 $, for every c-struct $\sigma$. Intuitively, a c-struct represents a set of sequences that are all equivalent up to the ordering of commutative commands (see~\cite{lamport-generalized} for a complete discussion on c-struct). In the rest of the paper, unless otherwise specified, the symbol $c$, possibly sub-scripted, ranges over commands, and the symbol $\mathcal{D}$, possibly sub-scripted, ranges over sets of commands.

@@

A dependency-set algorithm exposes the input interface $\texttt{announce}_p\left( c \right)$, to announce a command $c$, and the output interface $\texttt{suggest}_p \left( c,\mathcal{D}\right)$, to suggest a set of dependencies $\mathcal{D}$ for $c$, where $p\in P$ is the process executing the call.  
Moreover, a dependency-set algorithm must ensure that:
\begin{enumerate}[noitemsep,nolistsep]
    \item For any suggestion $\texttt{suggest}_p \left( c,\mathcal{D}\right)$, every command in $\{c\}\cup \mathcal{D}$ must have been announced before.
    \item For any two suggestions $\texttt{suggest}_p \left( c_1,\mathcal{D}_1\right)$ and $\texttt{suggest}_q \left( c_2,\mathcal{D}_2\right)$ (with $p$ possibly equal to $q$),  if $c_1$ and $c_2$ do not commute then either $c_1\in \mathcal{D}_2$ or $c_2 \in \mathcal{D}_1$.
\end{enumerate}

@@

A map-agreement algorithm exposes the input interface $\texttt{propose}_p\left( c, \mathcal{D} \right)$, to propose a set of dependencies $\mathcal{D}$ for a command $c$, and the output interface $\texttt{decide}_p\left( c, \mathcal{D} \right)$, to decide $\mathcal{D}$ for $c$, where $p\in P$ is the process executing the call.
Moreover, a map-agreement algorithm must ensure that: 
\begin{enumerate}[noitemsep,nolistsep]
    \item If the set of dependencies $\mathcal{D}$ is decided for a command $c$, then $\mathcal{D}$ has been proposed for $c$ at an earlier time.
    \item If $\mathcal{D}_1$ is decided for a command $c$ and $\mathcal{D}_2$ is decided for the same command $c$, then $\mathcal{D}_1$ is equal to $\mathcal{D}_2$.
 \end{enumerate}

@@

\begin{enumerate}[noitemsep,nolistsep]
    \item For any decision $\texttt{decide}_p\left( c, \mathcal{D} \right)$, then $\mathcal{D}$ has been proposed for $c$ at an earlier time.
    \item For any two decisions $\texttt{decide}_p\left( c, \mathcal{D}_1 \right)$, $\texttt{decide}_q\left( c, \mathcal{D}_2 \right)$ (with $p$ possibly equal to $q$), then $\mathcal{D}_1$ is equal to $\mathcal{D}_2$.

>>>>

We consider a set of processes $P$ subject to crash-stop faults and communicating by message-passing in an asynchronous network. Processes in $P$ must solve the Generalized Consensus problem~\cite{Lamport05GeneralizeConsensus}. Each process receives proposals for commands of the form $\operatorname{Propose}(c)$, and it produces responses of the form $\operatorname{Decide}(\sigma)$, where $\sigma$ is a c-struct. A c-struct set is a set, containing the element $\bot$, with an append operator
$\bullet$ such that $\sigma \bullet c$ is a c-struct, for any c-struct $\sigma$ and command $c$. We say that two commands \textit{commute} when $\sigma\bullet c_1\bullet c_2 =  \sigma\bullet c_2\bullet c_1 $, for every c-struct $\sigma$. Intuitively, a c-struct represents a set of sequences that are all equivalent up to the ordering of commutative commands (see~\cite{Lamport05GeneralizeConsensus} for a complete discussion on c-struct). In the rest of the paper, unless otherwise specified, the symbol $c$, possibly sub-scripted, ranges over commands, and the symbol $\mathcal{D}$, possibly sub-scripted, ranges over sets of commands.

@@

A dependency-set algorithm exposes the input interface $\operatorname{announce}_p\left( c \right)$, to announce a command $c$, and the output interface $\operatorname{suggest}_p \left( c,\mathcal{D}\right)$, to suggest a set of dependencies $\mathcal{D}$ for $c$, where $p\in P$ is the process executing the call.  
Moreover, a dependency-set algorithm must ensure that:
\begin{enumerate}[noitemsep,nolistsep]
    \item For any suggestion $\operatorname{suggest}_p \left( c,\mathcal{D}\right)$, every command in $\{c\}\cup \mathcal{D}$ must have been announced before.
    \item For any two suggestions $\operatorname{suggest}_p \left( c_1,\mathcal{D}_1\right)$ and $\operatorname{suggest}_q \left( c_2,\mathcal{D}_2\right)$ (with $p$ possibly equal to $q$),  if $c_1$ and $c_2$ do not commute then either $c_1\in \mathcal{D}_2$ or $c_2 \in \mathcal{D}_1$.
\end{enumerate}

@@

A map-agreement algorithm exposes the input interface $\operatorname{propose}_p\left( c, \mathcal{D} \right)$, to propose a set of dependencies $\mathcal{D}$ for a command $c$, and the output interface $\operatorname{decide}_p\left( c, \mathcal{D} \right)$, to decide $\mathcal{D}$ for $c$, where $p\in P$ is the process executing the call.
Moreover, a map-agreement algorithm must ensure that: 
\begin{enumerate}[noitemsep,nolistsep]
    \item If the set of dependencies $\mathcal{D}$ is decided for a command $c$, then $\mathcal{D}$ has been proposed for $c$ at an earlier time.
    \item If $\mathcal{D}_1$ is decided for a command $c$ and $\mathcal{D}_2$ is decided for the same command $c$, then $\mathcal{D}_1$ is equal to $\mathcal{D}_2$.
 \end{enumerate}

@@

\begin{enumerate}[noitemsep,nolistsep]
    \item For any decision $\operatorname{decide}_p\left( c, \mathcal{D} \right)$, then $\mathcal{D}$ has been proposed for $c$ at an earlier time.
    \item For any two decisions $\operatorname{decide}_p\left( c, \mathcal{D}_1 \right)$, $\operatorname{decide}_q\left( c, \mathcal{D}_2 \right)$ (with $p$ possibly equal to $q$), then $\mathcal{D}_1$ is equal to $\mathcal{D}_2$.
